Agile Formality: A Mole of Software Engineering Practices

### 2010-07-02 papers/ModelBasedTestCaseGenerationDataStreamProtocol/paper.tex
minimal update

% code coverage interpretation
The statement code coverage figures show that the test suites do a good job on the most important package, the \lil{StreamDriver}. 
The generated test suite reaches almost $ 80 \% $, while the handmade tests have only a slightly lower coverage ratio: $ 76 \% $. 
The combination of test suites raise the coverage ratio to $ 88.5 \% $. 
This is a clear indication that one test suite is not completely overlapping the other: the intuition that test suites are not alternatives, but they should be used together to achieve the higher benefits, is confirmed.
A similar indication is provided by \lil{SimulatorDriver} package as well.

>>>>

% code coverage interpretation
The statement code coverage figures show that the test suites do a good job on the most important package, the \lil{StreamDriver}. 
The generated test suite reaches almost $ 80 \% $, while the handmade tests have only a slightly lower coverage ratio: $ 76 \% $. 
The combination of test suites raise the coverage ratio to $ 88.5 \% $. 
This is a clear indication that one test suite is not completely overlapping the other: the intuition that test suites are not alternatives, but have to be used together to achieve the higher benefits, is confirmed.
A similar indication is provided by \lil{SimulatorDriver} package as well.
